Mendelian randomization for causal inference in Genome-wide association studies

### 2022-02-16 mr-review.Rmd
added refs from OMR paper

Recent research on the omnigenic hypothesis, which posits 
that every SNP's effect on a trait is nonzero, has informed
MR methods development [@Boyle2017]. @wang_mendelian_nodate 
recognized the limitations of previous MR methods in the 
context of the omnigenic hypothesis. To accommodate the possibility
that a trait is influenced by many genome-wide, small effects,

@@

>>>>

Recent research on the omnigenic hypothesis, which posits 
that every SNP's effect on a trait is nonzero, has informed
MR methods development [@Boyle2017]. @wang_mendelian_nodate 
recognized the limitations of previous MR methods in the 
context of the omnigenic hypothesis. To accommodate the possibility
that a trait is influenced by many SNPs, @wang_mendelian_nodate

@@

MR analysis has revealed causal relationships and led to mechanistic insights for many 
common diseases [@mancuso2017integrating;@parisinos2020genome;@zeng_causal_2019-2;@larsson2019smoking;@zheng2020phenome;@robinson2016insight;@luo2019association;@au2018impact;@zhao2019effect;@zeng_causal_2019;@zeng_causal_2019-1].
